\vspace{-0.2cm}
\cvsection{Projects}
\begin{cventries}
%     \cventry
%     {Research Intern, Big Data Experience Lab, Adobe Research}
%     {Semantic Matching (Meaning Learning)}
%     {Bangalore, India}
%     {May. 2018 - July. 2018}
%     {
%       \begin{cvitems}
%         \item {The project aimed at looking for different ways in which we can assist users of search systems in constructing queries that are richer and more likely to retrieve the desired results}
% \item{The research problem that was the focus of the internship was to use historical data (previous queries provided by users, the results that were returned, meta data about them, as well as interactions of the users with these results) to build machine learnt models that generate reformulation suggestions}
% \item{The solution built on published baseline models and research in these areas, requiring familiarity with current state-of-the-art literature in related areas like NLP}
% \item{Most of the experimentation was done via toolkits available in Python, TensorFlow and PyTorch}
%       \end{cvitems}
%     }
    \cventry
    {Course Project, Prof. Arnab Bhattacharya}
    {Document Similarity using Lexical Chains}
    {IIT Kanpur}
    {Jan. 2018 - April. 2018}
    {
      \begin{cvitems}
        \item {The project aimed at understanding the \textbf{meaning of a document} in a better manner inorder to improve the accuracy of models used for computing the similarities among documents}
        \item{Using semantic information extracted from ontology such as \textbf{WordNet} could help in understanding the meaning in a better manner}
        \item{Attempt towards integrating WordNet with lexical chains to alleviate common challenges, such as \textbf{synonymy and polysemy} and that of extracting core semantics from texts}
      \end{cvitems}
    }\\
    \vspace{2mm}
    \cventry
    {Course Project, Prof. Medha Atre}
    {Cycle Renting Web Application}
    {IIT Kanpur}
    {Jan. 2018 - April. 2018}
    {
      \begin{cvitems}
        \item {Developed a cycle renting web application based on \textbf{Django}}
        \item{Application users could send requests to other users, would get a notification about the status of their request, register their own cycles on the platform and rent them to other users}
      \end{cvitems}
    }\\
    \vspace{2mm}
%     \cventry
%     {Research Intern, Indian Institute of Science, Prof. Chandra Sekhar Seelamantula}
%     {Adaptive Frequency
% Estimation Using Iterative
% DESA with RDFT Based
% Filter}
%     {Bangalore, India}
%     {May. 2017 - July. 2017}
%     {
%       \begin{cvitems}
%         \item {Combined \textbf{Discrete Energy Separation Algorithm (DESA-1)} Algorithm and \textbf{Recursive Discrete Fourier Transform (RDFT)}-Based Filter to design a new technique for Grid Voltage Frequency Estimation}
%         \item {Proposed technique is computationally efficient and also robust to negative effects caused by noise and harmonics}
%         \item {Learnt about \textbf{DFT, FFT, DESA-1, DESA-1a, DESA-2,} Teager Energy Operator \textbf{(TEO)} and many other techniques involved in Instantaneous Frequency Estimation}
%       \end{cvitems}
%     }
    \cventry
    {Manufacturing Processes TA202A Project, Prof. Sounak K. Choudhary}
    {Biodegradable Systematic Manure Machine}
    {IIT Kanpur}
    {Jan. 2017 - April. 2017}
    {
      \begin{cvitems}
        \item {Built a Biodegradable Systematic Manure Machine using Manufacturing Processes such as \textbf{Drilling, Turning, Milling} etc.}
        \item {Aim of Machine is to reduce the biodegradable waste into smallest size possible}
        \item {Worked in a team of 8 members and a guide}
      \end{cvitems}
    }\\
    \vspace{2mm}
    \cventry
    {Manufacturing Processes TA201A Project , Prof. Rajiv Shekhar}
    {Beverage Can Vending Machine}
    {IIT Kanpur}
    {Aug. 2016 - Nov. 2016}
    {
      \begin{cvitems}
        \item {Built a Beverage Can Vending Machine using Manufacturing Processes such as \textbf{Welding, Brazing, Casting, Sheet Metal Working} etc.}
        \item {Aim of Machine is to dispense beverages to customers automatically, after the customer inserts currency or credit into the machine}
        \item {Worked in a team of 4 members, \textbf{1st team to attempt this project since years}}
      \end{cvitems}
    }
\end{cventries}
